Spin canonical divisors of log stacky curves

### 2015-06-22 stacky_write_up/spin_cring.tex
produced outline, reordered paper with filler intro

\section{Introduction}
\todo{Edit this stuff}
This is our project.
Example, stuff from Voight and Zureick-Brown \cite{vzb:stacky}
and O'Dorney's paper \cite{dorney:canonical}.
We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.

@@

\section{Background}
\todo{edit this}
Here are some definitions.
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.

\section{Effective Genus Zero Spin Divisors}
\label{sec:g_0_effective}
In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ 
when $\Delta$ is a non- zero effective divisor.  Using this, we can 
reduce to looking at effective stacky divisors.  Then, applying a 
result for general effective $\mathbf{Q}$ divisors, we deduce that $
R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with 
relations generated up to degree $2e$ with initial terms quadratic 
in the generators.  We also demonstrate that these bounds are tight 
up to \todo{insert how tight they are}.

First we prove a nice result about minimal generation of ideals of relations:

@@

\iffalse
\begin{lem}
\label{lem:minimal_quadratic_2}
Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
generated in degree 1 that are equipped with monomial ordering $\prec$.
 Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
\[
	\begin{tikzcd}
	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
Further suppose that $I'$ is generated over $I$ by elements $f_1,
\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
is of the form $y_i$.  Then, the elements $f_i$ determine minimal
generators for $I'$ over $I$.
\end{lem}

\begin{proof}
Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
\]
\[
	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
\]

\noindent
determines map of rings, no longer necessarily graded. 
By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent.  By the theory of Grobner basis,
\[
	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
\]
so
\[
	\dim_k (I'/I)_2=j.
\]
This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}
\fi

@@

\section{Non-effective Genus Zero Spin Divisors}
\label{sec:g_0_non_effective}

In this section, we will prove that if $(\sx , 0, L)$ is a spin curve,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; 0)$, then
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
e_r)$ with relations generated in degree at most $2e$, so long as $\sigma$
does not lie in a finite list of exceptions. This is proven in
Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather
involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in
Subsection ~\ref{ssec:g_0_base} we check the base cases of the
induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we
list out the exceptional cases.

@@

@@

\begin{enumerate}
	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{3\}$
	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
	\item[(d)] $\sigma_4 = (0; 5, 7, 7; 0), J_4 = \{2, 3\}$
	\item[(e)] $\sigma_5 = (0; 7, 7, 7; 0), J_5 = \{1, 2, 3\}$
	\item[(f)] $\sigma_6 = (0; 3, 3, 3, 5; 0), J_6 = \{4\}$
	\item[(g)] $\sigma_7 = (0; 3, 3, 5, 5; 0), J_7 = \{3, 4\}$
	\item[(h)] $\sigma_8 = (0; 3, 5, 5, 5; 0), J_8 = \{2, 3, 4\}$
	\item[(i)] $\sigma_9 = (0; 5, 5, 5, 5; 0), J_9 = \{1, 2, 3, 4\}$
	\item[(j)] $\sigma_{10} = (0; 3, 3, 3, 3, 3; 0), J_{10} = \{1, 2, 3, 4, 5\}$
\end{enumerate}

@@

	(c) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline

	(d) & \{3, 5, 5, 7, 7\} & \{10, 10, 12, 12, 14\}	& 7\\ \hline

	(e) & \{3, 5, 5, 7, 7, 7\} & \{10, 10, 10, 12, 12, 12, 14, 14, 14\}	& 7\\ \hline

	(f) & \{3, 3, 4, 5\} & \{8, 9\} & 5\\ \hline

	(g) & \{3, 3, 4, 5, 5\} & \{8, 8, 9, 9, 10\} & 5\\ \hline

	(h) & \{3, 3, 4, 5, 5, 5\} &
	\{8, 8, 8, 9, 9, 9, 10, 10, 10\} & 5\\ \hline

	(i) & \{3, 3, 4, 5, 5, 5, 5\} &
	\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\} & 5\\ \hline

	(j) &	\{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
\end{longtable}

@@

\begin{longtable}
	{| c | c || c | c | c |}
	\hline
	$\sigma$ & $J$ &  $i$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$\\
	\hline
	\hline

	$(0; 3, 3, 11; 0)$ & $\{3\}$ & $\forall i \in J$ & 1 & 0\\	\hline

	$(0; 3, 7, 7; 0)$ & $\{3\}$ & $\forall i \in J$ & 2 & 0\\ \hline

	$(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $\forall i \in J$ & 2 & 0\\ \hline

	$(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & $\forall i \in J$ & 3 & 0\\ \hline

	$(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $\forall i \in J$ & 2 & 0\\ \hline

	$(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $\forall i \in J$ & 3 & 0\\ \hline

	$(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $\forall i \in J$ & 4 & 0\\ \hline

	$(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $\forall i \in J$ & 5 & 0\\ \hline

	$(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $\forall i \in J$ & 5 & 0\\ \hline
\end{longtable}

@@

\ssec{Conclusion}
\label{ssec:g_0_conclusion}

@@

\section{Genus positive}

\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}

\section{Acknowledgements}
We are grateful to VZB.

>>>>

\section{Introduction}
\todo{Edit this stuff}
This is our project.
Modular Forms.

Example, stuff from Voight and Zureick-Brown \cite{vzb:stacky}
and O'Dorney's paper \cite{dorney:canonical}.

We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.

@@

\section{Background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
\todo{edit this}

\subsection{Definitions}
Here are some definitions.

\begin{defn}
\textbf{Saturations} of the canonical divisor, as defined in 7.
2 of VZB \cite{vzb:stacky}.
\end{defn}

\section{General Lemmata}
First we present the general inductive lemmata that will be applied
for all genera.

\ssec{General: quadratic initial ideal minimal relations}
First we prove a nice result about minimal generation of ideals of relations:

@@

%
%\begin{lem}
%\label{lem:minimal_quadratic_2}
%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
%generated in degree 1 that are equipped with monomial ordering $\prec$.
 %Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
%\[
	%\begin{tikzcd}
	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	%\end{tikzcd}
%\]
%Further suppose that $I'$ is generated over $I$ by elements $f_1,
%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
%is of the form $y_i$.  Then, the elements $f_i$ determine minimal
%generators for $I'$ over $I$.
%\end{lem}
%
%\begin{proof}
%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
%degree 1. Then,
%\[
	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
%\]
%\[
	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
%\]
%
%
%\noindent
%determines map of rings, no longer necessarily graded. 
%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent.  By the theory of Grobner basis,
%\[
	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
%\]
%so
%\[
	%\dim_k (I'/I)_2=j.
%\]
%This implies any set of
%generators for $I$ must have at least $j$ elements. Since $f_1,
%\ldots, f_j$ is such a set, it is minimal.
%\end{proof}
%

@@

TRANSITION
\todo{transition!}

@@

\section{Genus one}
We now consider the case when the genus is positive. The genus zero
case is the most complicated and reserve that for Section ~\ref{sec:g_0_effective}
and Section ~\ref{sec:g_0_non_effective}. We begin with the genus one case.

\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
We prove an inductive theorem on adding 2-sat here.
\todo{description}

\section{High genus}
Aaron will write amazing things here.

\section{Genus Zero Effective}
\label{sec:g_0_effective}
Now we consider the genus zero case.
\todo{write intro}

In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ 
when $\Delta$ is a non- zero effective divisor.  Using this, we can 
reduce to looking at effective stacky divisors.  Then, applying a 
result for general effective $\mathbf{Q}$ divisors, we deduce that $
R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with 
relations generated up to degree $2e$ with initial terms quadratic 
in the generators.  We also demonstrate that these bounds are tight 
up to \todo{insert how tight they are}.

We have Lemma ~\ref{lem:minimal_quadratic}.
\todo{fill in hole here}

\section{Genus Zero Non-effective}
\label{sec:g_0_non_effective}

In this section, we will prove that if $(\sx , 0, L)$ is a spin curve,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; 0)$, then
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
e_r)$ with relations generated in degree at most $2e$, so long as $\sigma$
does not lie in a finite list of exceptions. This is proven in
Subsection ~\ref{ssec:g_0_noneff_induction}. The proof is a rather
involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in
Subsection ~\ref{ssec:g_0_base} we check the base cases of the
induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we
list out the exceptional cases.

Here we describe induction of raising degrees from Theorem ~\ref{thm:ram_order_ind}
\todo{fill out}

@@

\begin{enumerate}
	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{3\}$
	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
	\item[(d)] $\sigma_4 = (0; 5, 5, 7; 0), J_4 = \{3\}$
	\item[(e)] $\sigma_5 = (0; 5, 7, 7; 0), J_5 = \{2, 3\}$
	\item[(f)] $\sigma_6 = (0; 7, 7, 7; 0), J_6 = \{1, 2, 3\}$
	\item[(g)] $\sigma_7 = (0; 3, 3, 3, 5; 0), J_7 = \{4\}$
	\item[(h)] $\sigma_8 = (0; 3, 3, 5, 5; 0), J_8 = \{3, 4\}$
	\item[(i)] $\sigma_9 = (0; 3, 5, 5, 5; 0), J_9 = \{2, 3, 4\}$
	\item[(j)] $\sigma_{10} = (0; 5, 5, 5, 5; 0), J_{10} = \{1, 2, 3, 4\}$
	\item[(k)] $\sigma_{11} = (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$
\end{enumerate}

@@

	(c) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline

	(d) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline

	(e) & \{3, 5, 5, 7, 7\} & \{10, 10, 12, 12, 14\}	& 7\\ \hline

	(f) & \{3, 5, 5, 7, 7, 7\} & \{10, 10, 10, 12, 12, 12, 14, 14, 14\}	& 7\\ \hline

	(g) & \{3, 3, 4, 5\} & \{8, 9\} & 5\\ \hline

	(h) & \{3, 3, 4, 5, 5\} & \{8, 8, 9, 9, 10\} & 5\\ \hline

	(i) & \{3, 3, 4, 5, 5, 5\} &
	\{8, 8, 8, 9, 9, 9, 10, 10, 10\} & 5\\ \hline

	(j) & \{3, 3, 4, 5, 5, 5, 5\} &
	\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\} & 5\\ \hline

	(k) &	\{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
\end{longtable}

@@

\begin{longtable}
	{| c | c | c || c | c |}
	\hline
	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$\\
	\hline
	\hline

	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & 1 & 0\\	\hline

	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & 1 & 0\\ \hline

	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & 2 & 0\\ \hline

	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & 1 & 0\\ \hline

	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & 2 & 0\\ \hline

	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & 3 & 0\\ \hline

	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & 2 & 0\\ \hline

	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & 3 & 0\\ \hline

	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & 4 & 0\\ \hline

	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & 5 & 0\\ \hline

	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & 5 & 0\\ \hline
\end{longtable}

@@

\ssec{Application of induction}
\label{ssec:g_0_noneff_induction}
Now we can combine this.

@@

\section{Acknowledgements}
We are grateful to David Zureick-Brown for introducing us to this
field of study, providing incredibly helpful guidance, and being an
excellent project mentor. We also thank Ken Ono and the Emory University
Number Theory REU for arranging our project and providing a great
environment for mathematical learning and collaboration. Finally, we
gratefully acknowledge that our research was financially supported by
NSF Grant \_\_\_\_\_ via the Emory University Number Theory REU. We deeply
appreciate all of the support that has made our work possible.
